A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/Process.lagda.tex
described link and cut

All the constructors except \AgdaInductiveConstructor{link} and
\AgdaInductiveConstructor{cut} basically follow the same pattern: they possibly
quantify over some types $A$ and $B$ and then (implicitly) over a typing context
$\Context$ through the function \AgdaFunction{∀[\_]} applied to a predicate of
the form $P~\AgdaFunction{⇒}~\AgdaDatatype{Proc}$. The predicate states how to
build a process that is well typed in $\Context$, provided that $\Context$
satisfies $P$. In general, $P$ is a (separating) conjunction of sub-predicates
corresponding to the channel on which the process is acting and to the premises
of its typing rule.

>>>>

The constructor \AgdaInductiveConstructor{link} models a process of the form
$\Link\x\y$. This process is well typed in a context of the form $x : A, y :
\dual{A}$, namely a context satisfying the predicate
$\AgdaDatatype{Ch}~A~\AgdaDatatype{∗}~\AgdaDatatype{Ch}~(\AgdaFunction{dual}~A)$
which we see on the left-hand side of \AgdaFunction{⇒}.
%
The constructor \AgdaInductiveConstructor{cut} models a cut $\Cut[A]\x{P}{Q}$.
For this process to be well typed in a context $\Context$, it must be the case
that $\Splitting\Context\ContextD\ContextE$ so that $P$ and $Q$ are well typed
in the contexts $x : A, \ContextD$ and $x : \dual{A}, \ContextE$ respectively.
Since $x$ is the most recently introduced channel, the types $A$ and $\dual{A}$
must be added \emph{at the front} of $\ContextD$ and $\ContextE$, which we do by
means of the functions $(A~\AgdaInductiveConstructor{∷\_})$ and
$(\AgdaFunction{dual}~A~\AgdaInductiveConstructor{∷\_})$ (these are partial
applications of the constructor $\AgdaInductiveConstructor{\_∷\_}$ for lists to
which we have supplied the left operand).

All the remaining constructors basically follow the same pattern: they possibly
quantify over some types $A$ and $B$ and then (implicitly) over a typing context
$\Context$ through the function \AgdaFunction{∀[\_]} applied to a predicate of
the form $P~\AgdaFunction{⇒}~\AgdaDatatype{Proc}$. The predicate states how to
build a process that is well typed in $\Context$, provided that $\Context$
satisfies $P$. In general, $P$ is a (separating) conjunction of sub-predicates
corresponding to the channel on which the process is acting and to the premises
of its typing rule.
